CUNY SPSS Data Science Math Homework 2

### 2018-07-21 data-science-math/Homework 2.Rmd
More progress on HW2

$$A=\frac{\{505\}}{\{1,2...539,540\}}=\frac{1}{540}\approx 0.0019$$

@@

$$P(h\cap nf)= \frac{52 \cdot \frac{1}{4}}{52-12}=\frac{13}{40}=0.325$$

@@

```{r q5, echo=FALSE}
q4_data <- data.frame(h=c('Apartment','Dorm','With Parent(s)','Sorority/Fraternity Home', 'Other'), Male = c(233, 159, 102, 220, 250), Female=c(208, 138, 280, 265, 146))
names(q4_data) <- c('','Male','Female')
emphasize.strong.cols(1)
```

```{r q5_table, results='asis'}
pandoc.table(q4_data)
```

@@

$$P(m) = \frac{233+159+102+120+250}{233+159+102+220+250+208+138+280+265+146} =\frac{964}{2001} \approx 0.4818 $$
```{r}
sum(q4_data$Male)/(sum(q4_data$Male)+sum(q4_data$Female))
```

@@

```{r q9, echo=FALSE}
q9_data <- data.frame(c=c('Freshman','Sophomores','Juniors','Seniors'), Male = c(12, 19, 12, 7), Female=c(12, 15, 4, 4))
names(q9_data) <- c('','Male','Female')
emphasize.strong.cols(1)
```

```{r q9_table, results='asis'}
pandoc.table(q9_data)
```

@@

$$P(fm|jf) = \frac{12}{84} \cdot \frac{4}{85} \approx 0.0068$$
```{r}
total_students <- sum(q9_data$Male) + sum(q9_data$Female)
12/(total_students-1) * 4/total_students
```

@@

@@

Consider the following data:
𝒙𝒙 5 6 7 8 9
𝒑𝒑(𝒙𝒙) 0.1 0.2 0.3 0.2 0.2

@@

Find the expected value $E(x)$ Round your answer to one decimal place.

@@

#### Step 3

Find the standard deviation. Round your answer to one decimal place.

#### Step 4

>>>>

$$P=\frac{\{505\}}{\{1,2...539,540\}}=\frac{1}{540}\approx 0.0019$$

@@

$$P(hnf)= \frac{52 \cdot \frac{1}{4}}{52-12}=\frac{13}{40}=0.325$$

@@

----------------------------------------------
            &nbsp;              Male   Female 
------------------------------ ------ --------
        **Apartment**           233     208

           **Dorm**             159     138

      **With Parent(s)**        102     280

 **Sorority/Fraternity Home**   220     265

          **Other**             250     146   
----------------------------------------------

@@

$$P(m) = \frac{233+159+102+120+250}{233+159+102+220+250+208+138+280+265+146} =\frac{964}{2001} \approx 0.4818 $$
```{r}
q4_data <- data.frame(h=c('Apartment','Dorm','With Parent(s)','Sorority/Fraternity Home', 'Other'), Male = c(233, 159, 102, 220, 250), Female=c(208, 138, 280, 265, 146))
sum(q4_data$Male)/(sum(q4_data$Male)+sum(q4_data$Female))
```

@@

--------------------------------
     &nbsp;       Male   Female 
---------------- ------ --------
  **Freshman**     12      12

 **Sophomores**    19      15

  **Juniors**      12      4

  **Seniors**      7       4    
--------------------------------

@@

$$P(fm|jf) = \frac{12}{84} \cdot \frac{4}{85} \approx 0.0068$$
```{r}
q9_data <- data.frame(c=c('Freshman','Sophomores','Juniors','Seniors'), Male = c(12, 19, 12, 7), Female=c(12, 15, 4, 4))
names(q9_data) <- c('','Male','Female')
total_students <- sum(q9_data$Male) + sum(q9_data$Female)
12/(total_students-1) * 4/total_students
```

@@

$$ C(13,7) = \frac{13!}{7!(13-7)!} =  \frac{6227020800}{5040\cdot 6!} = \frac{6227020800}{5040\cdot 720} = \frac{6227020800}{3628800} = 1716$$

```{r}
q22_data <- combinations(13,7)
nrow(q22_data)
```

@@

Consider the following data:

----------------------------------------
  &nbsp;    NA    NA    NA    NA    NA  
---------- ----- ----- ----- ----- -----
  **x**      5     6     7     8     9

 **P(x)**   0.1   0.2   0.3   0.2   0.2 
----------------------------------------

@@

Find the expected value $E(x)$ Round your answer to one decimal place.
$$E(x) = \Sigma {xP(x)}= (5 \times 0.1)+(6 \times 0.2)+(7 \times 0.3)+(8 \times 0.2)+(9 \times 0.2) = 7.2$$
```{r}
x <- c(5, 6, 7, 8, 9)
px <-c(0.1, 0.2, 0.3,  0.2, 0.2)
ex <- sum(x*px)
ex
```

@@

$$\sigma^2=\frac{\Sigma (x-E(x))^2}{N} = \frac{(5-7.2)^2+(6-7.2)^2+(7-7.2)^2+(8-7.2)^2+(9-7.2)^2}{5}$$
$$\sigma^2= \frac{4.84+1.44+0.04+0.64+3.24}{5}=\frac{10.2}{5}=2.04$$

```{r}
v <- sum((x-ex)**2)/length(x)
v
```
#### Step 3

Find the standard deviation. Round your answer to one decimal place.
$$\sigma = \sqrt{\sigma ^2} = \sqrt{2.04} \approx 1.4$$
```{r}
v**(1/2)
```

### Step 4
